---
knit: "bookdown::render_book"
---

\appendix

```{r setup-appendix, include=FALSE, cache = FALSE}
library(knitr)
read_chunk(here::here("case_study/analysis/analysis_code/mrp_fitting.R"))
read_chunk(here::here("case_study/analysis/analysis_code/mrp_vis.R"))
```

# Appendix 

## Supplementary Material

All of the codes used to conduct the analysis and produce the report is available in [this Github repository](https://github.com/Dewi-Amaliah/MRP_diagnostic_plot). Particularly, the code for data wrangling and preparation can be found [here](https://github.com/Dewi-Amaliah/MRP_diagnostic_plot/blob/main/case_study/analysis/cces_acs_wrangling.Rmd), and the code for MRP preparation and visualisation can be found [here](https://github.com/Dewi-Amaliah/MRP_diagnostic_plot/blob/main/case_study/analysis/mrp_fitting.R) and [here](https://github.com/Dewi-Amaliah/MRP_diagnostic_plot/blob/main/case_study/analysis/mrp_vis.R), respectively.

## Terms description {#terms}

There are some terms we used in Section {com-prac} that the readers might find unfamiliar with, especially in Figure \@ref(fig:common-plots), Figure \@ref(fig:common-axis), and Figure \@ref(fig:facet-plots). Hence Table \@ref(tab:terms-desc) displays the description of those terms. 

```{r terms-desc}
terms <- tribble(~Term, ~Description,
                 "dot plot", "Data is displayed by point/dot, one of the axis is categorical variable.",
                 "scatter plot", "Data is diplayed by point/dot, both x and y-axis are numeric.",
                 "choropleth map", "Thematic map coloured by the proportion of statistical variable it represents.",
                 "bar plot", "Data is displayed by rectangular bar, one of the axis is categorical variable.",
                 "histogram", "Similar to bar plot but number are grouped into ranges.",
                 "density plot", "Distribution of numerical variable, the y-axis is the kernel density estimates.", 
                 "other types", "Other plot types found in the reviewed articles, but the number is too few to be categorised as one category (boxplot, heatmap, bubble plot, and logit curve)",
                 "case", "The response variable that is estimated. It sometimes displayed as faceted plot, in which each panel represents different outcome/response variable. For example, a graph contains 2 facets, A and B are the MRP estimates for opinion regarding same-sex marriage and abortion, respectively. Hence, A and B are considered as case.",
                 "small area", "Estimates of subpopulation, geographically or demographically, for example estimates by state, county, gender, age group, education level, and religion. In some plots, it could also be another variable associates with the MRP estimates. For example, if MRP estimates used as predictor for another response variable and there is a visualisation display their relationship, then this variable is considered as small area.")

kable(terms, format = "latex",
      caption = "Terms description used in Systematic Literature Review result",
      booktabs = TRUE) %>%
  column_spec(2, width = "30em")
```


## Proportion of observations by states {#apd-state}

The following plots show the percentage of observations by state in CCES and ACS, respectively. 

```{r state-cces, fig.height = 6, fig.width = 5, fig.cap = "Distribution of observation in CCES data by state. The horizontal axis represents the percentage of the observations and the vertical axis represents the state ordered from the largest to lowest percentage of observations."}
```

```{r state-acs, fig.height = 6, fig.width = 5, fig.cap = "Distribution of observation in ACS data by state. The horizontal axis represents the percentage of the observations and the vertical axis represents the state ordered from the largest to lowest percentage of observations."}
```

## Additional Graphs

The following plots represent metrics and 95% credible interval visualisation as done in Section \@ref(vis-purp).

**Education**

Figure \@ref(fig:apd-educ-metrics) shows the metrics and Figure \@ref(fig:apd-ci-len-edu) shows the 95% comparison of credible interval length based on education level.

```{r apd-educ-metrics, fig.width=5, fig.height=6, fig.cap="Metrics of the model with edication as additional covariate. The benchmark is the baseline model, not the ground truth. Metrics of High school or less and Post-graduate categories are consistently have the higher deviance to the baseline model."}
```

```{r apd-ci-len-edu, fig.cap="The comparison of the 95 percent credible interval length between model with education as additional covariate and the baseline model by education levels. The credible interval of bigger model for Post-graduate category is slightly narrower compared to the baseline model.", out.width = "90%"}
```

\newpage

**Age (The estimation using the model with education as additional covariate)**

Figure \@ref(fig:apd-age-fit2) shows the metrics and Figure \@ref(fig:apd-age-ci-fit2) shows the 95% comparison of credible interval length based on age group (the comparison is between the model with education as additonal covariate and the baseline model).

```{r apd-age-fit2, fig.width=5, fig.height=6, fig.cap="Metrics of the model with education as additional covariate. The benchmark is the baseline model, not the ground truth."}
```

```{r apd-age-ci-fit2, fig.cap = "The comparison of the 95 percent credible interval length between model with education as additional covariate and the baseline model by education levels. The lenght of credible interval between the two model fits is pretty much the same.", out.width = "90%"}
```

\newpage

**Age (The estimation using the model with more race categories)**

Figure \@ref(fig:apd-age-fit3) shows the metrics and Figure \@ref(fig:apd-age-ci-fit3) shows the 95% comparison of credible interval length based on age group (the comparison is between the model with more race categories and the baseline model).

```{r apd-age-fit3, fig.width=5, fig.height=6, fig.cap="Metrics of the model with more race categories. The benchmark is the baseline model, not the ground truth."}
```

```{r apd-age-ci-fit3, fig.cap = "The comparison of the 95 percent credible interval length between model with more race categories and the baseline model by education levels. The lenght of credible interval between the two model fits is pretty much the same.", out.width = "90%"}
```


