---
title: "Prelimenary Result"
author: "Dewi Lestari Amaliah - 31251587"
date: "17/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(kableExtra)
library(patchwork)
library(ggthemes)
```


```{r}
papers <- read_csv(here::here("sis_literature_review/paper_metadata/metadata_july_22.csv"))
```

# Result 

### Plot type - whether it is diagnostic plot or not 

```{r}
papers <- papers %>%
  mutate(Diagnostic = as.factor(Diagnostic))

papers %>%
  group_by(Diagnostic) %>%
  count() %>%
  mutate(pct = round(n/nrow(papers) * 100, 2)) %>%
  kable() %>%
  kable_styling()
```


### The facets

```{r}
filter_facet_all <- papers %>%
  filter(Facets > 1) %>%
  pivot_longer(c(Facet_x, Facet_y), names_to = "facet_axis", values_to = "facet_type") %>%
  group_by(facet_type) %>%
  count()

ggplot(filter(filter_facet_all, !is.na(facet_type))) +
  geom_bar(aes(x = reorder(facet_type, -n), y = n), stat = "identity") +
  theme(axis.text.x = element_text(angle = 10)) +
  xlab("whats in the facet") +
  ylab("count") +
  ggtitle("Overall facet")
```

### Plot types

```{r}
plot_type_sum <- papers %>%
  mutate(uncertainty = ifelse(str_detect(plot_type, "error|CI bar|CIB"), "yes", "no"),
         plot_type = as.factor(plot_type)) %>%
  mutate(plot_type_wrangled = fct_collapse(plot_type, `bar plot` = c("bar & dot plot with error bar", 
                                                                     "bar plot"),
                                           `dot plot` = c("dot plot", 
                                                          "dot plot with CI bar", 
                                                          "dot plot with CIB", 
                                                          "dot plot with error bar"),
                                           `line plot` = c("line and dot plot", 
                                                           "line and dot plot with error bar", 
                                                           "line plot"),
                                           `scatter plot` = c("scatter plot with error bar", 
                                                              "scatter plot"),
                                           `histogram & density plot` = c("density plot",
                                                                          "histogram with density plot",
                                                                          "histogram"),
                                           `other` = c("boxplot",
                                                       "bubble plot",
                                                       "heatmap",
                                                       "logit curve")
                                           )) %>%
  mutate(diagnostic = ifelse(Diagnostic == 0, "Communication", "Diagnostic")) %>%
  mutate(plot_type_wrangled = factor(plot_type_wrangled, levels = c("other", 
                                                                    "histogram & density plot",
                                                                    "bar plot",
                                                                    "choropleth map",
                                                                    "line plot", 
                                                                    "scatter plot",
                                                                    "dot plot")))
```

```{r}
ggplot(plot_type_sum) +
  geom_bar(aes(y = plot_type_wrangled, fill = uncertainty), position="stack") +
  facet_wrap(~diagnostic) +
  theme(legend.position = "bottom") +
  ylab(" ") +
  xlab(" ") +
  scale_fill_manual(values = c("#585858", "#DA81F5")) +
  theme_classic()
```





```{r}
ggplot(papers) +
  geom_bar(aes(y = plot_type, fill = Diagnostic)) +
  facet_wrap(~Diagnostic) +
  theme(legend.position = "none") +
  ylab(" ") +
  xlab(" ") 
```

In this plot, 0 means "communication plot"; 1 means "diagnostic plot"


### Axis type in Communication Plot

```{r}
axis_complot <- filter(papers, Diagnostic == 0) %>% 
  group_by(x_axis, y_axis) %>% count()

tile_com <- ggplot(axis_complot, aes(x_axis, y_axis, fill = n)) + 
  geom_tile() +
  ylab("values in y-axis") +
  xlab("values in x-axis") +
  labs(fill = "number of plots") +
  theme_classic() +
  ggtitle("a) Communication plots") +
  theme(plot.title = element_text(size = 11),
        legend.title = element_text(size = 9),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9))
```


If we make it detailed further to the plot type, the result is as follows:

```{r}
filter(papers, Diagnostic == 0) %>% 
  group_by(x_axis, y_axis, plot_type) %>% count() %>% 
  kable(caption = "The summary of axis in communication plot with the plot type") %>% 
  kable_styling() 
```



### Axis Type in Diagnostic Plots

```{r}

axis_diaplot <- filter(papers, Diagnostic == 1) %>% 
  group_by(x_axis, y_axis) %>% count() 

tile_diag <- ggplot(axis_diaplot, aes(x_axis, y_axis, fill = n)) + 
  geom_tile() +
  ylab("values in y-axis") +
  xlab("values in x-axis") +
  labs(fill = "number of plots") +
  theme_classic() +
  ggtitle("b) Diagnostic plots") +
  theme(axis.text.x = element_text(angle = 30)) +
  theme(plot.title = element_text(size = 11),
        legend.title = element_text(size = 9),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9))
  
```

```{r}
tile_com + tile_diag + plot_layout(nrow = 2)
```



The summary of x_axis and y_axis including the plot type is: 

```{r}
filter(papers, Diagnostic == 1) %>% 
  group_by(x_axis, y_axis, plot_type) %>% count() %>% 
  kable(caption = "The summary of axis in diagnostic plot with the plot type") %>% 
  kable_styling()
```










### Colors

```{r}
ggplot(papers) + 
  geom_bar(aes(y = color, fill = Diagnostic)) +
  facet_wrap(~Diagnostic) +
  ggtitle("Type of Color")
```


### Shapes

```{r}
ggplot(papers) + 
  geom_bar(aes(y = shape, fill = Diagnostic)) +
  facet_wrap(~Diagnostic) +
  ggtitle("Type of Shapes")
```

### Performance Criteria 

```{r}
paper_perf_crit <- papers %>%
  filter(performance_criteria_bias !=0 |
           performance_criteria_correlation != 0 |
           perfomance_criteria_MAE !=0 |
           performance_criteria_SE != 0 |
           `performance_criteria_MSE/RMSE` != 0) %>%
  pivot_longer(c(performance_criteria_bias,
                 performance_criteria_correlation,
                 perfomance_criteria_MAE,
                 `performance_criteria_MSE/RMSE`,
                 performance_criteria_SE), names_to = "perf_crit",
               values_to = "is_use_perf_crit") %>%
  mutate(metrics = case_when(str_detect(perf_crit, "bias") ~ "bias",
                             str_detect(perf_crit, "correlation") ~ "correlation",
                             str_detect(perf_crit, "MAE") ~ "MAE",
                             str_detect(perf_crit, "MSE") ~ "MSE/RMSE",
                             str_detect(perf_crit, "SE") ~ "SE")) %>%
  mutate(is_use_perf_crit = as.factor(is_use_perf_crit),
         metrics = factor(metrics, levels = c("MAE", "bias", "correlation", "MSE/RMSE", "SE")))

ggplot(paper_perf_crit, aes(fill=is_use_perf_crit, x=metrics)) + 
  geom_bar(position="stack") +
  xlab("performance criteria") +
  scale_fill_manual(values = c("#BDC3C7", "#17A589")) +
  theme_classic() +
  theme(legend.position = "none")
```

There are 29 (out of 123) plots that use performance criteria as its feature. 
The turquoise color represents the number of plots that use corresponding performance criteria. 
Most of the plots using bias as their performance criteria. 

Regarding, the plot type, plots with performance criteria mostly incorporate dot plots.

```{r}
paper_perf_crit_wide <- papers %>%
  filter(performance_criteria_bias !=0 |
           performance_criteria_correlation != 0 |
           perfomance_criteria_MAE !=0 |
           performance_criteria_SE != 0 |
           `performance_criteria_MSE/RMSE` != 0)

ggplot(paper_perf_crit_wide) +
  geom_bar(aes(y = plot_type)) +
  ggtitle("plot type using performance criteria")

```



### What estimates are compared with MRP?

```{r}
paper_comp <- papers %>%
  filter(comparison_MRP != 0 |
           comparison_other_method != 0 |
           comparison_other_study != 0 |
           comparison_raw != 0 |
           comparison_truth != 0 |
           comparison_weight != 0) %>%
  pivot_longer(c(comparison_MRP,
                 comparison_other_method,
                 comparison_other_study,
                 comparison_raw,
                 comparison_truth, comparison_weight),
                 names_to = "comp_with",
                 values_to = "is_comp_with") %>%
  mutate(comp = case_when(str_detect(comp_with, "MRP") ~ "MRP",
                             str_detect(comp_with, "method") ~ "other method",
                             str_detect(comp_with, "study") ~ "other study",
                             str_detect(comp_with, "raw") ~ "raw",
                             str_detect(comp_with, "truth") ~ "truth",
                             str_detect(comp_with, "weight") ~ "weight")) %>%
  mutate(is_comp_with = as.factor(is_comp_with),
         comp = factor(comp, levels = c("raw","truth", "MRP", "other study", "weight", "other method")))

ggplot(paper_comp, aes(fill=is_comp_with, x=comp)) + 
  geom_bar(position="stack") +
  xlab("comparison of MRP estimates with") +
  scale_fill_manual(values = c("#bababa", "#2c7bb6")) +
  theme_classic() +
  theme(legend.position = "none")
```

There are 67 plots (out of 123) that use comparison as its feature. 
The turquoise color represent the number of plots using corresponding comparison. 
Most of them compare the MRP estimates with the raw data. 


```{r}
paper_comp_wide <- papers %>%
  filter(comparison_MRP != 0 |
           comparison_other_method != 0 |
           comparison_other_study != 0 |
           comparison_raw != 0 |
           comparison_truth != 0 |
           comparison_weight != 0)

ggplot(paper_comp_wide) +
  geom_bar(aes(y = plot_type)) +
  ggtitle("plot type of comparison plots")


```



