---
title: "CCES_application"
author: "Dewi Lestari Amaliah - 31251587"
date: "21/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(forcats)
library(data.table)
```

Needs:

1. Ground truth from election results.
2. Weight estimates from CCES
3. Couple of different MRP estimates, i.e., :

- Base model
- Model with additional predictors
- Model with more levels
- Model with a slightly different outcome


Steps:
1. Clean the CCES data with the 5 demographic variables
2. Clean the ACS data <- make sure it is inline with the CCES
3. Use the PERWT/3 to get the take the estimates of the subgroup total from the 3 years of survey 

Next week goal:
1. Munging the data so it could be used until the mapping stage in mrpkit. 


## Munging the CCES data

```{r}
cces <- haven::read_dta(here::here("data/cces16.dta")) 

#age
#sex
#education
#race_ethnicity <- collapse Native American + Middle Eastern + Other to be Other
#state

cces_use <- cces %>%
  select(V101, commonweight, commonweight_post, inputstate, birthyr, gender, educ, race, hispanic, pid3,
         CC16_364c, CC16_364b, CC16_410a, CC16_410a_nv) %>%
  mutate(age_orig = 2016 - birthyr) %>%
  as_factor() %>%
  mutate(race = as.character(race),
         hispanic = as.character(hispanic)) %>%
  # change the label if the respondent said yes in hispanic origin
  mutate(race_ethnicity = ifelse(hispanic == "No" | is.na(hispanic), race, "Hispanic")) %>%
  mutate(race_ethnicity_collp = fct_collapse(race_ethnicity,
                                             Other = c("Native American", "Middle Eastern", "Other")),
         age = as_factor(case_when(age_orig >= 18 & age_orig <= 25 ~ "18-25",
                         age_orig > 25 & age_orig <= 35 ~ "26-35",
                         age_orig > 35 & age_orig <= 45 ~ "36-45",
                         age_orig > 45 & age_orig <= 55 ~ "46-55",
                         age_orig > 55 & age_orig <= 65 ~ "56-65",
                         age_orig > 65 & age_orig <= 75 ~ "66-75",
                         age_orig > 75 ~ "76 years and over")))


# write_rds(cces_use, "cces_use.rds")
```


## Munging the ACS data


```{r}
# acs_2015_a <- fread(here::here("data/ss15pusa.csv"))
# acs_2015_b <- fread(here::here("data/ss15pusb.csv"))
# 
# acs_15 <- rbind(acs_2015_a, acs_2015_b) %>%
#   mutate(year = 2015)
# 
# write_rds(acs_15, "acs_15.rds", compress = "gz")
```

```{r}
# acs_2016_a <- fread(here::here("data/ss16pusa.csv"))
# acs_2016_b <- fread(here::here("data/ss16pusb.csv"))
# 
# acs_16 <- rbind(acs_2016_a, acs_2016_b) %>%
#   mutate(year = 2016)
# 
# write_rds(acs_16, "acs_16.rds", compress = "gz")
```

```{r}
acs_2017_a <- fread(here::here("data/psam_pusa_2017.csv"))
acs_2017_b <- fread(here::here("data/psam_pusb_2017.csv"))

acs_17 <- rbind(acs_2017_a, acs_2017_b) %>%
  mutate(year = 2017)

# write_rds(acs_17, "acs_17.rds", compress = "gz")
```

```{r}
acs_15 <- readRDS("acs_15.rds")
acs_16 <- readRDS("acs_16.rds")
acs_17 <- readRDS("acs_17.rds")

# select the variable that will only be used in the analysis

acs_15_use <- acs_15 %>%
  select(SERIALNO, ST, PWGTP, SCHL, SEX, RAC1P, HISP, AGEP, year)

acs_16_use <- acs_16 %>%
  select(SERIALNO, ST, PWGTP, SCHL, SEX, RAC1P, HISP, AGEP, year)

acs_17_use <- acs_17 %>%
  select(SERIALNO, ST, PWGTP, SCHL, SEX, RAC1P, HISP, AGEP, year)

# bind the three years
acs_use <- bind_rows(acs_15_use, acs_16_use, acs_17_use)
# write_rds(acs_use, "acs_use.rds", compress = "gz")
```

```{r}
# recode the variables in cces data since they are coded in integer 

acs <- read_rds("acs_use.rds")
acs_race <- acs %>%
  # include Hispanic in the race and ethnicity variable
  # if someone is identified has hispanic descendant, he/she will be coded to Hispanic
  mutate(RAC1P_ethnic = ifelse(HISP != 1, 10, RAC1P))

acs_use <- acs_race %>%
  mutate(state = as_factor(case_when(ST == 1 ~ "Alabama",
                           ST == 2 ~ "Alaska",
                           ST == 4 ~ "Arizona",
                           ST == 5 ~ "Arkansas",
                           ST == 6 ~ "California",
                           ST == 8 ~ "Colorado",
                           ST == 9 ~ "Connecticut",
                           ST == 10 ~ "Delaware",
                           ST == 11 ~ "District of Columbia",
                           ST == 12 ~ "Florida",
                           ST == 13 ~ "Georgia",
                           ST == 15 ~ "Hawaii",
                           ST == 16 ~ "Idaho",
                           ST == 17 ~ "Illinois",
                           ST == 18 ~ "Indiana",
                           ST == 19 ~ "Iowa",
                           ST == 20 ~ "Kansas",
                           ST == 21 ~ "Kentucky",
                           ST == 22 ~ "Louisiana",
                           ST == 23 ~ "Maine",
                           ST == 24 ~ "Maryland",
                           ST == 25 ~ "Massachusetts",
                           ST == 26 ~ "Michigan",
                           ST == 27 ~ "Minnesota",
                           ST == 28 ~ "Mississippi",
                           ST == 29 ~ "Missouri",
                           ST == 30 ~ "Montana",
                           ST == 31 ~ "Nebraska",
                           ST == 32 ~ "Nevada",
                           ST == 33 ~ "New Hampshire",
                           ST == 34 ~ "New Jersey",
                           ST == 35 ~ "New Mexico",
                           ST == 36 ~ "New York",
                           ST == 37 ~ "North Carolina",
                           ST == 38 ~ "North Dakota",
                           ST == 39 ~ "Ohio",
                           ST == 40 ~ "Oklahoma",
                           ST == 41 ~ "Oregon",
                           ST == 42 ~ "Pennsylvania",
                           ST == 44 ~ "Rhode Island",
                           ST == 45 ~ "South Carolina",
                           ST == 46 ~ "South Dakota",
                           ST == 47 ~ "Tennessee",
                           ST == 48 ~ "Texas",
                           ST == 49 ~ "Utah",
                           ST == 50 ~ "Vermont",
                           ST == 51 ~ "Virginia",
                           ST == 53 ~ "Washington",
                           ST == 54 ~ "West Virginia",
                           ST == 55 ~ "Wisconsin",
                           ST == 56 ~ "Wyoming",
                           ST == 72 ~ "Puerto Rico")),
         educ = as_factor(case_when(SCHL == 1 ~ "No schooling completed",
                          SCHL == 2 ~ "Nursery schoool, preschool",
                          SCHL == 3 ~ "Kindergarten",
                          SCHL == 4 ~ "Grade 1",
                          SCHL == 5 ~ "Grade 2",
                          SCHL == 6 ~ "Grade 3",
                          SCHL == 7 ~ "Grade 4",
                          SCHL == 8 ~ "Grade 5",
                          SCHL == 9 ~ "Grade 6",
                          SCHL == 10 ~ "Grade 7",
                          SCHL == 11 ~ "Grade 8",
                          SCHL == 12 ~ "Grade 9",
                          SCHL == 13 ~ "Grade 10",
                          SCHL == 14 ~ "Grade 11",
                          SCHL == 15 ~ "12th grade - no diploma",
                          SCHL == 16 ~ "Regular high school diploma",
                          SCHL == 17 ~ "GED or alternative credential",
                          SCHL == 18 ~ "Some college, but less than 1 year",
                          SCHL == 19 ~ "1 or more years of college credit. no degree",
                          SCHL == 20 ~ "Associate's degree",
                          SCHL == 21 ~ "Bachelor's degree",
                          SCHL == 22 ~ "Master's degree",
                          SCHL == 23 ~ "Professional degree beyond a bachelor's degree",
                          SCHL == 24 ~ "Doctorate degree")),
         gender = as_factor(case_when(SEX == 1 ~ "Male",
                            SEX == 2 ~ "Female")),
         race_ethnicity = as_factor(case_when(RAC1P_ethnic == 1 ~ "White alone",
                          RAC1P_ethnic == 2 ~ "Black or African American alone",
                          RAC1P_ethnic == 3 ~ "American Indian alone",
                          RAC1P_ethnic == 4 ~ "Alaska Native alone",
                          RAC1P_ethnic == 5 ~ "American Indian and Alaska Native tribes",
                          RAC1P_ethnic == 6 ~ "Asian alone",
                          RAC1P_ethnic == 7 ~ "Native Hawaiian and Other Pacific Islander alone",
                          RAC1P_ethnic == 8 ~ "Some Other Race alone",
                          RAC1P_ethnic == 9 ~ "Two or More Races",
                          RAC1P_ethnic == 10 ~ "Hispanic")),
         age = as_factor(case_when(AGEP < 18 ~ "Less than 18 years",
                                   AGEP >= 18 & AGEP <= 25 ~ "18-25",
                                   AGEP > 25 & AGEP <= 35 ~ "26-35",
                                   AGEP > 35 & AGEP <= 45 ~ "36-45",
                                   AGEP > 45 & AGEP <= 55 ~ "46-55",
                                   AGEP > 55 & AGEP <= 65 ~ "56-65",
                                   AGEP > 65 & AGEP <= 75 ~ "66-75",
                                   AGEP > 75 & AGEP <= 90 ~ "76-90",
                                   AGEP > 90 ~ "over 90 years")))
```


```{r}
# collapse the levels in factor variable
acs_use_collapse <- acs_use %>%
  mutate(educ_collps = fct_collapse(educ, `No high school` = c("No schooling completed",
                                                                "Nursery schoool, preschool",
                                                                "Kindergarten",
                                                                "Grade 1",
                                                                "Grade 2",
                                                                "Grade 3",
                                                                "Grade 4",
                                                                "Grade 5",
                                                                "Grade 6",
                                                                "Grade 7",
                                                                "Grade 8",
                                                                "Grade 9",
                                                                "Grade 10",
                                                                "Grade 11",
                                                                "12th grade - no diploma"),
                                     `Some college` = c("GED or alternative credential",
                                                        "Some college, but less than 1 year",
                                                        "1 or more years of college credit. no degree"),
                                     `Post-graduate` = c("Master's degree",
                                                         "Professional degree beyond a bachelor's degree",
                                                         "Doctorate degree")),
         race_ethnicity_collps = fct_collapse(race_ethnicity, Other = c("American Indian alone",
                                                       "Alaska Native alone",
                                                       "American Indian and Alaska Native tribes",
                                                       "Native Hawaiian and Other Pacific Islander alone",
                                                       "Some Other Race alone")),
         wt = PWGTP/3) %>%
  select(SERIALNO, ST, wt, year, HISP, AGEP, state, educ, educ_collps,
         gender,race_ethnicity,race_ethnicity_collps, age)

# write_rds(acs_use_collapse, "acs_use_wrangled.rds")
```


Next week goal: Build the models 
Netx week goal 2: 2. Interpete/write paragraph of the result 

Outcome: Party, past vote, and future vote


1. Base model: age, race_ethnicity (collapsed race_ethnicity), state -> outcome would be future vote 
2. Additonal predictor: base model + education 
3. Model with additional level: all of the race_ethnicity/non-collapsed race_ethnicity (work with the ACS data to get the hispanic) if someone answer white+hispanic -> hispanic -> outcome would be future vote 
4. Model 2 with 3 different outcome i.e., future vote (CC16_410a), early vote (CC16_364b), and party preference (pid3).

Also: Inspect the time ellapsed to run every method when using mrpkit



