---
title: "mrp_build"
author: "Dewi Lestari Amaliah - 31251587"
date: "03/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mrpkit)
library(brms)
library(tidyverse)
library(tictoc)
```

## Using mrpkit to build model

1. Base model: age, race_ethnicity (collapsed race_ethnicity), state, gender. Outcome would be future vote 
2. Additional predictor: Base model + education
3. Model with additional level: age, race_ethnicity (original race_ethnicity), state, gender. Outcome would be future vote
4. Model 2 with 3 different outcome , i.e., future vote (CC16_410a), early vote (CC16_364b), and party preference (pid3).

```{r}
# read the data

cces <- read_rds("cces_use.rds")
acs <- read_rds("acs_use_wrangled.rds")
```

## Model 1

Model 1 is the base model, with age, race_ethnicity (collapsed race_ethnicity), and state as the predictor. The outcome would be the future vote. 

```{r surveydata}
# pre-process the cces data for base model
cces_mrp1 <- cces %>%
  # rename variable as mrpkit workflow
  rename(wt = commonweight) %>%
  mutate(vote_post_nonbinary = as.character(CC16_410a)) %>%
  # mutate the outcome which is vote for Donald Trump (yes/no)
  mutate(vote_post = as.factor(ifelse(vote_post_nonbinary == "Donald Trump (Republican)", "yes", "no"))) %>%
  mutate(race_ethnicity = as_factor(race_ethnicity)) %>%
  select(age, inputstate, race_ethnicity_collp, race_ethnicity, gender, educ, vote_post, wt)

# drop the level since we don't want any unused level be in the SurveyData object
cces_mrp1$gender <- droplevels(cces_mrp1$gender)
cces_mrp1$inputstate <- droplevels(cces_mrp1$inputstate)
cces_mrp1$educ <- droplevels(cces_mrp1$educ)


#### CREATE SURVEYDATA OBJECT
# create survey data object for the survey data
cces_mod1 <- SurveyData$new(
  data = cces_mrp1,
  questions = list(age = "Respondent's age group",
                   inputstate = "State",
                   race_ethnicity_collp = "Respondent's race/ethnicity collapsed Native American, Middle Eastern, and Other to Other",
                   race_ethnicity = "Respondent's race/ethnicity original level",
                   gender = "Respondent's gender",
                   educ = "Respondent's education",
                   vote_post = "Whether the respondent vote for Donald Trump in 2016 President vote (Post)"),
  responses = list(age = levels(cces_mrp1$age),
                   inputstate = levels(cces_mrp1$inputstate),
                   race_ethnicity_collp = levels(cces_mrp1$race_ethnicity_collp),
                   race_ethnicity = levels(cces_mrp1$race_ethnicity),
                   gender = levels(cces_mrp1$gender),
                   educ = levels(cces_mrp1$educ),
                   vote_post = c("no", "yes")),
 weights = "wt")
# this step: 0.039 sec elapsed


# pre-process the acs data for base model
acs_mrp <- acs %>%
  # filter out the respondents whose age < 18 years because they are not in the scope of CCES survey?
  filter(age != "Less than 18 years") %>%
  select(state, wt, age, gender, race_ethnicity, race_ethnicity_collps, educ_collps)

acs_mrp$age <- droplevels(acs_mrp$age)

# create survey data object for the post-stratification data 
acs_data <- SurveyData$new(
  data = acs_mrp,
  questions = list(age = "Respondent's age group",
                   state = "State",
                   gender = "Respondent's gender",
                   race_ethnicity_collps = "Respondent's race/ethnicity recoded",
                   race_ethnicity = "Respondent's race/ethnicity",
                   educ_collps = "Respondent's highest educational attainment"),
  responses = list(age = levels(acs_mrp$age),
                   state = levels(acs_mrp$state),
                   gender = levels(acs_mrp$gender),
                   race_ethnicity_collps = levels(acs_mrp$race_ethnicity_collps),
                   race_ethnicity = levels(acs_mrp$race_ethnicity),
                   educ_collps = levels(acs_mrp$educ_collps)),
  weights = "wt"
)
# this step: 0.641 sec elapsed

# print the object
acs_data$print()
# this step: 58.992 sec elapsed
```


**Note:**
1. Re-check if using the `inputstate` (pre-election state name) or inputstate_post (post-election state name)

```{r questionmapping}

#### QUESTION MAPPING
q_age <- QuestionMap$new(
  name = "age",
  col_names = c("age", "age"),
  values_map = list(
    "18-25" = "18-25",
    "26-35" = "26-35",
    "36-45" = "36-45",
    "46-55" = "46-55",
    "56-65" = "56-65",
    "66-75" = "66-75",
    "76 years and over" = "76-90",
    "76 years and over" = "over 90 years"))

q_state <- QuestionMap$new(
  name = "state",
  col_names = c("inputstate", "state"),
  values_map = list(
    "Alabama" = "Alabama",
    "Alaska" = "Alaska",
    "Arizona" = "Arizona",
    "Arkansas" = "Arkansas",
    "California" = "California",
    "Colorado" = "Colorado",
    "Connecticut" = "Connecticut",
    "Delaware" = "Delaware",
    "District of Columbia" = "District of Columbia",
    "Florida" = "Florida",
    "Georgia" = "Georgia",
    "Hawaii" = "Hawaii",
    "Idaho" = "Idaho",
    "Illinois" = "Illinois",
    "Indiana" = "Indiana",
    "Iowa" = "Iowa",
    "Kansas" = "Kansas",
    "Kentucky" = "Kentucky",
    "Louisiana" = "Louisiana",
    "Maine" = "Maine",
    "Maryland" = "Maryland",
    "Massachusetts" = "Massachusetts",
    "Michigan" = "Michigan",
    "Minnesota" = "Minnesota",
    "Mississippi" = "Mississippi",
    "Missouri" = "Missouri",
    "Montana" = "Montana",
    "Nebraska" = "Nebraska",
    "Nevada" = "Nevada",
    "New Hampshire" = "New Hampshire",
    "New Jersey" = "New Jersey",
    "New Mexico" = "New Mexico",
    "New York" = "New York",
    "North Carolina" = "North Carolina",
    "North Dakota" = "North Dakota",
    "Ohio" = "Ohio",
    "Oklahoma" = "Oklahoma",
    "Oregon" = "Oregon",
    "Pennsylvania" = "Pennsylvania",
    "Rhode Island" = "Rhode Island",
    "South Carolina" = "South Carolina",
    "South Dakota" = "South Dakota",
    "Tennessee" = "Tennessee",
    "Texas" = "Texas",
    "Utah" = "Utah",
    "Vermont" = "Vermont",
    "Virginia" = "Virginia",
    "Washington" = "Washington",
    "West Virginia" = "West Virginia",
    "Wisconsin" = "Wisconsin",
    "Wyoming" = "Wyoming"))

q_gender <- QuestionMap$new(
  name = "gender",
  col_names = c("gender", "gender"),
  values_map = list(
    "Male" = "Male",
    "Female" = "Female"))

q_recollapsed <- QuestionMap$new(
  name = "collapsed_re",
  col_names = c("race_ethnicity_collp", "race_ethnicity_collps"),
  values_map = list(
    "Asian" = "Asian alone",
    "Black" = "Black or African American alone",
    "Hispanic" = "Hispanic",
    "Other" = "Other",
    "Mixed" = "Two or More Races",
    "White" = "White alone"))

q_re <- QuestionMap$new(
  name = "original_re",
  col_names = c("race_ethnicity", "race_ethnicity"),
  values_map = list(
    "White" = "White alone",
    "Asian" = "Asian alone",
    "Hispanic" = "Hispanic",
    "Black" = "Black or African American alone",
    "Mixed" = "Two or More Races",
    "Native American" = "American Indian and Alaska Native tribes",
    "Native American" = "American Indian alone",
    "Native American" = "Alaska Native alone",
    "Other" = "Some Other Race alone",
    "Other" = "Native Hawaiian and Other Pacific Islander alone",
    "Middle Eastern" = "Some Other Race alone"))

q_educ <- QuestionMap$new(
  name = "education",
  col_names = c("educ", "educ_collps"),
  values_map = list(
    "No HS" = "No high school",
    "High school graduate" = "Regular high school diploma",
    "Some college" = "Some college",
    "2-year" = "Associate's degree",
    "4-year" = "Bachelor's degree",
    "Post-grad" = "Post-graduate"))
```

```{r}
## SURVEY MAPPING STEP
map_model <- SurveyMap$new(sample = cces_mod1,
                            population = acs_data,
                            q_age,
                            q_state,
                            q_gender,
                            q_recollapsed, 
                            q_re,
                            q_educ)

map_model$validate()
map_model$mapping()
map_model$tabulate()

# Recheck: Is it okay to map all the variable here even though it is not included in the model?

### FIT THE MODEL

# Model 1
tic()
fit1 <- map_model$fit(
  fun = brms::brm,
  formula = vote_post ~ (1|age) + (1|gender) + (1+state) + (1|collapsed_re),
  family = "bernoulli",
  refresh = 100,
  cores = 2,
  backend = "cmdstanr"
)
toc()
# Total execution time: 26589.7 seconds.

# save the model 
saveRDS(fit1, "fit1.rds")
```

```{r}
fit1_predict <- fit1$population_predict()
# 65.759 sec elapsed
```

# Model 2

```{r}
# Model 2
tic()
fit2 <- map_model$fit(
  fun = brms::brm,
  formula = vote_post ~ (1|age) + (1|gender) + (1+state) + (1|collapsed_re) + (1|education),
  family = "bernoulli",
  refresh = 100,
  cores = 2,
  backend = "cmdstanr"
)
toc()
```


# Model 3
```{r}
tic()
fit3 <- map_model$fit(
  fun = brms::brm,
  formula = vote_post ~ (1|age) + (1|gender) + (1+state) + (1|original_re),
  family = "bernoulli",
  refresh = 100,
  cores = 2,
  backend = "cmdstanr"
)
toc()
```


# Model 4

## Model 4a: Model 2 with early vote as the outcome

```{r}
# pre-process the cces data for base model
cces_mrp2 <- cces %>%
  # rename variable as mrpkit workflow
  rename(wt = commonweight) %>%
  mutate(vote_early_nonbinary = as.character(CC16_364b)) %>%
  # mutate the outcome which is vote for Donald Trump (yes/no)
  mutate(vote_early = as.factor(ifelse(vote_early_nonbinary == "Donald Trump (Republican)", "yes", "no"))) %>%
  mutate(race_ethnicity = as_factor(race_ethnicity)) %>%
  select(age, inputstate, race_ethnicity_collp, race_ethnicity, gender, educ, vote_early, wt)

# drop the level since we don't want any unused level be in the SurveyData object
cces_mrp2$gender <- droplevels(cces_mrp2$gender)
cces_mrp2$inputstate <- droplevels(cces_mrp2$inputstate)
cces_mrp2$educ <- droplevels(cces_mrp2$educ)

#### CREATE SURVEYDATA OBJECT
# create survey data object for the survey data
cces_mod2 <- SurveyData$new(
  data = cces_mrp2,
  questions = list(age = "Respondent's age group",
                   inputstate = "State",
                   race_ethnicity_collp = "Respondent's race/ethnicity collapsed Native American, Middle Eastern, and Other to Other",
                   race_ethnicity = "Respondent's race/ethnicity original level",
                   gender = "Respondent's gender",
                   educ = "Respondent's education",
                   vote_early = "Whether the respondent vote for Donald Trump in 2016 President vote (Early)"),
  responses = list(age = levels(cces_mrp1$age),
                   inputstate = levels(cces_mrp1$inputstate),
                   race_ethnicity_collp = levels(cces_mrp1$race_ethnicity_collp),
                   race_ethnicity = levels(cces_mrp1$race_ethnicity),
                   gender = levels(cces_mrp1$gender),
                   educ = levels(cces_mrp1$educ),
                   vote_early = c("no", "yes")),
 weights = "wt")

# Here, we don't have to make the new survey object for the post-stratification data
# And directly go to mapping?

map_model4a <- SurveyMap$new(sample = cces_mod2,
                            population = acs_data,
                            q_age,
                            q_state,
                            q_gender,
                            q_recollapsed, 
                            q_re,
                            q_educ)

map_model4a$validate()
map_model4a$mapping()
map_model4a$tabulate()

tic()
fit4a <- map_model4a$fit(
  fun = brms::brm,
  formula = vote_early ~ (1|age) + (1|gender) + (1+state) + (1|collapsed_re) + (1|education),
  family = "bernoulli",
  refresh = 100,
  cores = 2,
  backend = "cmdstanr"
)
toc()
```


## Model 4b: Model 2 with party identity as the outcome

```{r}
# pre-process the cces data for base model
cces_mrp3 <- cces %>%
  # rename variable as mrpkit workflow
  rename(wt = commonweight) %>%
  mutate(party_nonbinary = as.character(pid3)) %>%
  # mutate the outcome which is Republican or not
  mutate(party = as.factor(ifelse(party_nonbinary == "Republican", "yes", "no"))) %>%
  mutate(race_ethnicity = as_factor(race_ethnicity)) %>%
  select(age, inputstate, race_ethnicity_collp, race_ethnicity, gender, educ, party, wt)

# drop the level since we don't want any unused level be in the SurveyData object
cces_mrp3$gender <- droplevels(cces_mrp3$gender)
cces_mrp3$inputstate <- droplevels(cces_mrp3$inputstate)
cces_mrp3$educ <- droplevels(cces_mrp3$educ)

#### CREATE SURVEYDATA OBJECT
# create survey data object for the survey data
cces_mod3 <- SurveyData$new(
  data = cces_mrp3,
  questions = list(age = "Respondent's age group",
                   inputstate = "State",
                   race_ethnicity_collp = "Respondent's race/ethnicity collapsed Native American, Middle Eastern, and Other to Other",
                   race_ethnicity = "Respondent's race/ethnicity original level",
                   gender = "Respondent's gender",
                   educ = "Respondent's education",
                   party = "Whether the respondent identify him/herself as Republican or not"),
  responses = list(age = levels(cces_mrp1$age),
                   inputstate = levels(cces_mrp1$inputstate),
                   race_ethnicity_collp = levels(cces_mrp1$race_ethnicity_collp),
                   race_ethnicity = levels(cces_mrp1$race_ethnicity),
                   gender = levels(cces_mrp1$gender),
                   educ = levels(cces_mrp1$educ),
                   party = c("no", "yes")),
 weights = "wt")

# Here, we don't have to make the new survey object for the post-stratification data
# And directly go to mapping?

map_model4b <- SurveyMap$new(sample = cces_mod3,
                            population = acs_data,
                            q_age,
                            q_state,
                            q_gender,
                            q_recollapsed, 
                            q_re,
                            q_educ)

map_model4b$validate()
map_model4b$mapping()
map_model4b$tabulate()

tic()
fit4b <- map_model4b$fit(
  fun = brms::brm,
  formula = party ~ (1|age) + (1|gender) + (1+state) + (1|collapsed_re) + (1|education),
  family = "bernoulli",
  refresh = 100,
  cores = 2,
  backend = "cmdstanr"
)
toc()
```


## Question to clarify:

1. Re-check if using the `inputstate` (pre-election state name) or inputstate_post (post-election state name)
2. Regarding the binary outcome, is it okay if it is vote Donald Trump/not?
3. For the early vote outcome, there are probably more NAs then the vote_post (future vote).
4. Recheck: Is it okay to map all the variable here even though it is not included in the model?
5. Is it okay to keep using the question mapping from the base model even though the outcomes are different?